\begin{thebibliography}{11} %This number should be higher than the number of entries in the bibliography because reasons...
%	\bibitem{id}
%		Author(s) Last name, First name, Company/Organisation, Year. Full Title
	\bibitem{feedback}
			Dodds, Stephen J., University of East London, 2015. Feedback Control: Linear, Nonlinear and Robust Techniques and Design with Industrial Applications.
	\bibitem{z7010}
			Xilinx, Nov. 2015. Zynq-7000 All Programmable SoC (Z-7010, Z-7015 and Z-7020): DC and AC Switching Characteristics.
	\bibitem{bootstrap_paper}
			Fairchild, Dec. 2014, Design and Application Guide of Bootstrap Circuit for High-Voltage Gate-Driver IC.
	\bibitem{DRV8301}
			Texas Instruments, Aug. 2013, DRV8301 - Three Phase Pre-Driver with Dual Current Shunt Amplifiers and Buck Regulator (datasheet).
	\bibitem{IRF4468PbF}
			International Rectifier, IRFP4468PbF Power MOSFET datasheet
	\bibitem{power_switching_converters}
			Neacsu, Dorin O., 2016, Power-Switching Converters: Medium and High Power-Switching 
	\bibitem{adc}
		Xilinx, May. 2015, 7 Series FPGAs and Zynq-7000 All Programmable SoC XADC Dual 12-Bit 1 MSPS Analog-to-Digital Converter (User Guide).	
	\bibitem{superB}
		Super B Lithium batteries, SB12V20P-FC Lightweight Lithium ion starter battery datasheet
	\bibitem{zynq_reference}
		Xilinx, February. 2015, Zynq-7000 All Programmable SoC (Technical Reference Manual).
	\bibitem{third_harmonic_injection}
		Suda, Barath Kumar; David, James, Eaton Corporation, Mar 'A Novel Third Harmonic Injection Method for Closed Loop Control of PMSM Motors'
	\bibitem{pmac_equivalent_diagram}
		A. B. Dehkordi, Student Member, IEEE, A. M. Gole, Senior Member, IEEE, T. L. Maguire, Senior Member, IEEE; 'Permanent Magnet Synchronous Machine Model for
		Real- Time Simulation'
	\bibitem{TO_247}
		Vishay Siliconix, July. 2013, TO-247AC (High Voltage) Package Information
	\bibitem{gokart_constant}
		Biancolini, Marco Evangelos, Department of Mechanical Engineering Tor Vergata University, 'Evaluation Of Aerodynamic Drag Of Go Kart By Means Of Coast Down Test And Cfd Analysis'
	\bibitem{wire_inductance}
		Thomsen, Mark, 1999, IEEE, 'Tricks of the Trade: Guesstimating Inductance of Wire Loops'
	\bibitem{electric_motor_and_drives}
		Austin Hughes, Bill Drury; 'Electric Motors and Drives: Fundamentals, Types and Applications - Fourth Edition'


\end{thebibliography}