%!TEX root = ../main.tex
\section{Introduction}

The expeditiously evolution in all technology areas has brought great results and helped vertically the humanity in all the aspects of modern life. \todo[inline]{does not make sense}
After overcoming numerous technical challenges and tries the result was in early 1910's to have the first three phase motors to the market.
\todo[inline]{Tesla invented the induction motor in 1889, and magnets weren't developed until the 1930's. Where does that decade come from? Kyriakos: Hitachi inveted the firts 3phase motors at early 10's, I refere you to reference No7}
This was the beginning of motor industry's activities in the field of electric motors as well as its starting point in motor technology development. 
Now, a century later, the electric motor has become a key device that underpins society in a wide range of fields including power generation, industry, transport, and home appliances\cite{Evolution}.
\\

Electronics engineering constituted part of this evolution, which combine the energy control with the participation of  active electrical components such as transistors, diodes integrated circuits, and associated passive electrical components. 
In particular, all the above  are inextricably linked with Brushless permanent DC (BLDC, PMAC) motors which is very important since they are more robust, have higher torque, higher efficiency, lower noise, lower EMI generation compared to brushed motors.
\todo{compared to induction motor, they have higher power density - torque are likely the same, efficiency } 
Since the electrical commutation of the motors are more complex and requires knowledge of the rotor position, an electrical motor controller is required to keep the motor spinning. \todo{and start spinning.}
\\

In this paper are going to combined all the fundamental electronic knowledge of courses learned during the previous  semester like Drives \& Controls,Power Electronics, Embedded Systems in order to replace and manufacture from the beginning the Sevcon gen4 motor control used in SDU electrical kart given. The main requirements of the project are given below. 




